---
title: "DAY2"
author: "Anel Lopez Gonzalez"
date: "2024-January"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#libraries
library(GEOquery)
library(edgeR)
library(limma)
library(NOISeq)
library(DESeq2)
library(clusterProfiler)
library(org.Hs.eg.db)
library(RColorBrewer)
library(gplots)
library(msigdbr)
library(magrittr)
```

## Experimental design

Lets review experimental design from a practical perspective

```{r read data}
# Read data
urld <- "https://www.ncbi.nlm.nih.gov/geo/download/?format=file&type=rnaseq_counts"
path <- paste(urld, "acc=GSE198256", "file=GSE198256_raw_counts_GRCh38.p13_NCBI.tsv.gz", sep="&");
GSE198256_count <- as.matrix(data.table::fread(path, header=T, colClasses="integer"), rownames=1)

# Read Meta data with GEOquery
gds <- getGEO("GSE198256")
Meta_GSE198256 <- pData(gds$GSE198256_series_matrix.txt.gz@phenoData)
Group <- Meta_GSE198256[,c("disease state:ch1")]

dim(GSE198256_count)
Group
```

## Limma: Normalize and set design

```{r Normalize and set design}
# set DGE class with edgeR and limma
dge <- DGEList(counts=GSE198256_count)

# Make sure on the metadata
rownames(Meta_GSE198256)==colnames(GSE198256_count)
Group[Group=="Covid19: Acute infection"] <- "Covid19AI"
Group[Group=="Covid19: Recovery 3Mo"] <- "Covid193Mo"
Group[Group=="Covid19: Recovery 6Mo"] <- "Covid196Mo"
design <- model.matrix(~ Group )
colnames(design) <- c("Intercept","Covid196Mo","Covid19AI","Healthy")

# Filter
keep <- filterByExpr(dge, design=design, min.count=10)
dge <- dge[keep,keep.lib.sizes=FALSE]

# Normalization
dge <- calcNormFactors(dge)
```

## Limma: Voom or Trend?

```{r Voom or Trend}
## Trend

# If the sequencing depth is reasonably consistent across the RNA samples, then the simplest and most robust approach to differential exis to use limma-trend. This approach will usually work well if the ratio of the largest library size to the smallest is not more than about 3-fold.
logCPM <- cpm(dge, log=TRUE, prior.count=3)
 # The prior count is used here to damp down the variances of logarithms of low counts.
fit <- lmFit(logCPM, design)

fit <- eBayes(fit, trend=TRUE)
 # logical, should an intensity-dependent trend be allowed for the prior variance? If FALSE then the prior variance is constant. Alternatively, trend can be a row-wise numeric vector, which will be used as the covariate for the prior variance.
 # The use of eBayes or treat with trend=TRUE is known as the limma-trend method (Law et al, 2014; Phipson et al, 2016). With this option, an intensity-dependent trend is fitted to the prior variances s2.prior
topTable(fit, coef=ncol(design))
trend_res <- topTable(fit,sort="none",n=Inf) #all the genes
## Voom

# When the library sizes are quite variable between samples, then the voom approach is theoretically more powerful than limma-trend.
v <- voom(dge, design, plot=TRUE)
# The voom method is similar in purpose to the limma-trend method, which uses eBayes or treat with trend=TRUE. The voom method incorporates the mean-variance trend into the precision weights, whereas limma-trend incorporates the trend into the empirical Bayes moderation. The voom method takes into account the sequencing depths (library sizes) of the individual columns of counts and applies the mean-variance trend on an individual observation basis. limma-trend, on the other hand, assumes that the library sizes are not wildly different and applies the mean-variance trend on a genewise basis. As noted by Law et al (2014), voom should be more powerful than limma-trend if the library sizes are very different but, otherwise, the two methods should give similar results.
fit <- lmFit(v, design)
fit <- eBayes(fit)
topTable(fit, coef=ncol(design))

voom_res <- topTable(fit,sort="none",n=Inf) #all the genes
```

## ACTIVITY 1:

-   How would you compare the results between voom and trend?

We could compare the fold changes found by the two methods. We could compare the number of genes identified as differentially expressed genes according to a treshold.

-   Is it required to run more than analysis?

According to the Vignette of limma, its enough to fit the linear model (lmFit) and then doing the statistical analysis (eBayes). Then you can filter the results tables according to specifies tresholds.

-   What exactly are we asking with this differential expression?

Since we do not specify any contrast, the default comparison will be the intercept, in this case 3 months recovery, against every other group.  

```{r ACTIVITY 1}
##TREND with contrasts
fit.t <- lmFit(logCPM, design)

contrast.matrix <- makeContrasts(Covid19AI-Healthy, Healthy, 
                                 Covid196Mo-Healthy,    
                                 levels=design)

fit.t2 <- contrasts.fit(fit.t, contrast.matrix)
fit.t2 <- eBayes(fit.t2, trend=TRUE) #dgea by empirical bayes moderation

# Store all of them
trend1 <- topTable(fit.t2,coef=1,sort="none",n=Inf) 
trend2 <- topTable(fit.t2,coef=2,sort="none",n=Inf)
trend3 <- topTable(fit.t2,coef=3,sort="none",n=Inf)

##VOOM
v <- voom(dge, design)

fit <- lmFit(v, design) #linear model for each gene

fit2 <- contrasts.fit(fit, contrast.matrix)
fit2 <- eBayes(fit2) #dgea by empirical bayes moderation

# Store all of them
voom1 <- topTable(fit2,coef=1,sort="none",n=Inf) 
voom2 <- topTable(fit2,coef=2,sort="none",n=Inf)
voom3 <- topTable(fit2,coef=3,sort="none",n=Inf)

#plot the logFC
#coef 1
plot(voom1$logFC, trend$logFC)

#coef 2
plot(voom2$logFC, trend2$logFC)

#coef 3
plot(voom3$logFC, trend3$logFC)
```

## ACTIVITY 2:

-   Plan the next analysis: questions, steps,...

```{r ACTIVITY 2}
# Add more contrasts
v <- voom(dge, design, plot=TRUE)
#colnames(design) <- c("Intercept","Covid196Mo","Covid19AI","Healthy")
fit <- lmFit(v, design) #linear model for each gene

contrast.matrix <- makeContrasts(Covid19AI-Healthy, Healthy, 
                                 Covid196Mo-Healthy,    
                                 levels=design)

fit2 <- contrasts.fit(fit, contrast.matrix)
fit2 <- eBayes(fit2) #dgea by empirical bayes moderation
topTable(fit2) 
topTable(fit2,coef=1) 
topTable(fit2,coef=2) 
topTable(fit2,coef=3) 
# topTable(fit2,coef=4) try this!
#Will not run because there is no 4th contrast specified

# Store all of them
DEG_AI_Healthy <- topTable(fit2,coef=1,sort="none",n=Inf) 
DEG_Healthy <- topTable(fit2,coef=2,sort="none",n=Inf)
DEG_6Mo_Healthy <- topTable(fit2,coef=3,sort="none",n=Inf)
```

## ORA and Gene Set Enrichment analysis.

-   What do we need to do the analysis?

For ORA, a set of DEGs and a universe or background (all the genes used to make the analysis). For GSEA, we need all the genes with their respective fold change and sorted, irrespective if they are differentially regulated or not. 

-   What are the tools required?

We need an annotation fo the organism under study (libraries such as org.Hs.eg.db for human) and a package that allows us to find overrepresentation of our set of genes in an annotation. 

```{r Prepare ORA and GSEA}
#keytypes(org.Hs.eg.db)

# If we want to shift annotations:
ENSEMBL_vector <- mapIds(
  # Replace with annotation package for the organism relevant to your data
  org.Hs.eg.db,
  # The vector of gene identifiers we want to map
  keys = rownames(GSE198256_count),
  # Replace with the type of gene identifiers in your data
  keytype = "ENTREZID",
  # Replace with the type of gene identifiers you would like to map to
  column = "ENSEMBL",
  # In the case of 1:many mappings, return the
  # first one. This is default behavior!
  multiVals = "first"
)

# We would like a data frame we can join to the differential expression stats
gene_key_df <- data.frame(
  ensembl_id = ENSEMBL_vector,
  entrez_id = names(ENSEMBL_vector),
  stringsAsFactors = FALSE
) %>%
  # If an Ensembl gene identifier doesn't map to a gene symbol, drop that
  # from the data frame
  dplyr::filter(!is.na(ensembl_id))
```

## Lets conduct ORA.

```{r Run ORA}
# Step 1: determine genes of interest.
diff_table <- topTable(fit2,coef=1,p.value=0.01,number=10000) 
genes_dif<- rownames(diff_table )

# Step 2: determine background.

background_set <- unique(rownames(logCPM))

# Step 3: Determine gene sets.

#msigdbr_species()
hs_msigdb_df <- msigdbr(species = "Homo sapiens")
head(hs_msigdb_df)

hs_kegg_df <- hs_msigdb_df %>%
  dplyr::filter(
    gs_cat == "C2", # This is to filter only to the C2 curated gene sets
    gs_subcat == "CP:KEGG" # This is because we only want KEGG pathways
  )

# Step 4: conduct ORA.

kegg_ora_results <- enricher(
  gene = genes_dif, # A vector of your genes of interest
  pvalueCutoff = 0.1, # Can choose a FDR cutoff
  pAdjustMethod = "BH", # Method to be used for multiple testing correction
  universe = background_set, # A vector containing your background set genes
  # The pathway information should be a data frame with a term name or
  # identifier and the gene identifiers
  TERM2GENE = dplyr::select(
    hs_kegg_df,
    gs_name,
    human_entrez_gene
  )
)

# Step 5: Visualize / explore

enrich_plot <- enrichplot::dotplot(kegg_ora_results)
enrich_plot

upset_plot <- enrichplot::upsetplot(kegg_ora_results)
upset_plot

# Step 6: EXERCISE: alternatives to KEGG?
#Use GO:BP
hs_gobp_df <- hs_msigdb_df %>%
  dplyr::filter(
    gs_subcat == "GO:BP" # This is because we only want KEGG pathways
  )

gobp_ora_results <- enricher(
  gene = genes_dif, # A vector of your genes of interest
  pvalueCutoff = 0.1, # Can choose a FDR cutoff
  pAdjustMethod = "BH", # Method to be used for multiple testing correction
  universe = background_set, # A vector containing your background set genes
  # The pathway information should be a data frame with a term name or
  # identifier and the gene identifiers
  TERM2GENE = dplyr::select(
    hs_gobp_df,
    gs_name,
    human_entrez_gene
  )
)

enrich_plot2 <- enrichplot::dotplot(gobp_ora_results)
enrich_plot2

upset_plot2 <- enrichplot::upsetplot(gobp_ora_results)
upset_plot2

# note: see mor examples: https://alexslemonade.github.io/refinebio-examples/03-rnaseq/pathway-analysis_rnaseq_01_ora.html#46_Over-representation_Analysis_(ORA) 
```

## Lets conduct GSEA.

```{r run GSEA}
# Step 1: determine genes of interest.
diff_table_all <- topTable(fit2,coef=1,p.value=1,number=nrow(logCPM)) 

list_ordered <- diff_table_all$logFC
names(list_ordered) <- rownames(diff_table_all)
list_ordered <- na.omit(list_ordered)
list_ordered <- sort(list_ordered, decreasing = TRUE)

# Step 4: conduct GSEA
list_ordered <- diff_table_all[,"logFC"]
names(list_ordered) <- rownames(diff_table_all)
  
gsea_results <- GSEA(
  geneList = list_ordered, # Ordered ranked gene list
  minGSSize = 25, # Minimum gene set size
  maxGSSize = 500, # Maximum gene set set
  pvalueCutoff = 0.05, # p-value cutoff
  eps = 0, # Boundary for calculating the p value
  seed = TRUE, # Set seed to make results reproducible
  pAdjustMethod = "BH", # Benjamini-Hochberg correction
  TERM2GENE = dplyr::select(
    hs_kegg_df,
    gs_name,
    human_entrez_gene
  )
)

# Step 5: Visualize / explore

head(gsea_results@result)

gsea_result_df <- data.frame(gsea_results@result)
gsea_result_df %>%
  # This returns the 3 rows with the largest NES values
  dplyr::slice_max(NES, n = 3)

most_positive_nes_plot <- enrichplot::gseaplot(
  gsea_results,
  geneSetID = "KEGG_SYSTEMIC_LUPUS_ERYTHEMATOSUS",
  title = "KEGG_SYSTEMIC_LUPUS_ERYTHEMATOSUS",
  color.line = "#0d76ff"
)
most_positive_nes_plot

gsea_result_df %>%
  # Return the 3 rows with the smallest (most negative) NES values
  dplyr::slice_min(NES, n = 3)

most_negative_nes_plot <- enrichplot::gseaplot(
  gsea_results,
  geneSetID = "KEGG_GRAFT_VERSUS_HOST_DISEASE",
  title = "KEGG_GRAFT_VERSUS_HOST_DISEASE",
  color.line = "#0d76ff"
)
most_negative_nes_plot

# Step 6: EXERCISE: alternatives to KEGG?
#We can use the same GO_BP we used for ORA

gsea_results2 <- GSEA(
  geneList = list_ordered, # Ordered ranked gene list
  minGSSize = 25, # Minimum gene set size
  maxGSSize = 500, # Maximum gene set set
  pvalueCutoff = 0.05, # p-value cutoff
  eps = 0, # Boundary for calculating the p value
  seed = TRUE, # Set seed to make results reproducible
  pAdjustMethod = "BH", # Benjamini-Hochberg correction
  TERM2GENE = dplyr::select(
    hs_gobp_df,
    gs_name,
    human_entrez_gene
  )
)

#require(enrichplot)
#require(ggplot2)
#require(stringr)
#dotplot(gsea_results2, showCategory=10, split=".sign", font.size = 10) 

# Step 7: EXERCISE: compare GSEA vs ORA?

#They are a different ways of finding patterns in our data, nevertheless I would expect some overlap in the results.


idx <- gsea_results2@result$ID %in% gobp_ora_results@result$ID

gsea_results2@result[idx,]
```

## Lets conduct GeneSetCluster.

```{r prepare GSEA}
# Healthy vs Group Covid19 
# We prepare a function from the previous analysis

# Healthy vs Covid19AI 
Diff_HvsAI <- topTable(fit2,coef=1,p.value=1,number=nrow(logCPM))
# Healthy vs Covid196Mo 
Diff_Hvs6Mo <- topTable(fit2,coef=3,p.value=1,number=nrow(logCPM))


hs_msigdb_df <- msigdbr(species = "Homo sapiens")
hs_kegg_df <- hs_msigdb_df %>%
  dplyr::filter(
    gs_cat == "C2", # This is to filter only to the C2 curated gene sets
    gs_subcat == "CP:KEGG" # This is because we only want KEGG pathways
  )


doGSEA <- function(diff_table) {
  list_ordered <- diff_table[,"B"]
  names(list_ordered) <- rownames(diff_table)
  
  return(GSEA(
    geneList = list_ordered, # Ordered ranked gene list
    minGSSize = 25, # Minimum gene set size
    maxGSSize = 500, # Maximum gene set set
    pvalueCutoff = 0.05, # p-value cutoff
    eps = 0, # Boundary for calculating the p value
    seed = TRUE, # Set seed to make results reproducible
    pAdjustMethod = "BH", # Benjamini-Hochberg correction
    TERM2GENE = dplyr::select(
      hs_kegg_df,
      gs_name,
      human_entrez_gene
    )
  ))
}

GSEA_HvsAI <- doGSEA(Diff_HvsAI)
GSEA_Hvs6Mo <- doGSEA(Diff_Hvs6Mo)

path <- "."

write.csv(GSEA_HvsAI, file = paste0(path, "/GSEA_HvsAI.csv"), row.names = FALSE)
write.csv(GSEA_Hvs6Mo, file = paste0(path, "/GSEA_Hvs6Mo.csv"), row.names = FALSE)
```

##GeneSetCluster

```{r run GeneSetCluster}
library(GeneSetCluster)
GSEA.files <- paste0(path, "/", list.files(path, pattern = ".csv"))

# Load the data and create Pathway object
# Automatically for GSEA, GREAT or IPA
GSEA.Object1 <- LoadGeneSets(file_location = GSEA.files, 
                              groupnames= c("GSEA_Hvs6Mo", "GSEA_HvsAI"), # names of the groups
                              P.cutoff = 0.05, # cut off the p.adjust
                              Mol.cutoff = 15, # minimum number of genes per pathway
                              Source = "GSEA", # the analysis (GSEA, GREAT or IPA)
                              structure = "ENTREZID", # Gene type (SYMBOL, ENTREZID, ENSEMBLID)
                              Organism = "org.Hs.eg.db", # database: Homo Sapiens or Mus musculus
                              seperator = "/") # the separator used for listing genes

# IMPORTANT when created manually, it is assumed that the pathways have been filtered by p-value and minimum number of genes per pathway
# Make sure you have filtered your data
GSEA.Object1Manual <- ObjectCreator(Pathways = c(GSEA_HvsAI@result$ID, 
                                                 GSEA_Hvs6Mo@result$ID),
                                    Molecules = c(GSEA_HvsAI@result$core_enrichment, 
                                                  GSEA_Hvs6Mo@result$core_enrichment),
                                    Groups = c(rep("GSEA_HvsAI", times=nrow(GSEA_HvsAI@result)), 
                                               rep("GSEA_Hvs6Mo", times=nrow(GSEA_Hvs6Mo@result))),
                                    Pvalues = c(GSEA_HvsAI@result$p.adjust,  # optional
                                                GSEA_Hvs6Mo@result$p.adjust),
                                    enrichmentScore = c(GSEA_HvsAI@result$NES, # optional
                                                        GSEA_Hvs6Mo@result$NES), 
                                    structure = "ENTREZID", Type = "", sep = "/",
                                    Source = "GSEA", organism = "org.Hs.eg.db")

GSEA.Object2 <- CombineGeneSets(Object = GSEA.Object1,
                                combineMethod = "Standard", threads = 8)


OptimalGeneSets(Object = GSEA.Object2, 
                uniquePathway = FALSE, # consider all the pathways (also repeated) or the unique pathways
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters")

OptimalGeneSets(Object = GSEA.Object2, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters")
# in both cases the optimal cluster is 2

GSEA.Object3 <- ClusterGeneSets(Object = GSEA.Object2, 
                                clusters = 2, # consider all the pathways (also repeated) or the unique pathways
                                method = "Hierarchical", # Hierarchical clustering or kmeans
                                order = "cluster",
                                molecular.signature = "All")

# plot results for both all pathways and unique pathways
plotnounique <- PlotGeneSets(GSEA.Object3, 
                             uniquePathways = FALSE, 
                             wordcloud = FALSE, # wordcloud only supported for GO terms
                             doORA = T) # do ora per cluster

plotunique <- PlotGeneSets(GSEA.Object3, 
                           uniquePathways = TRUE, 
                           wordcloud = FALSE, # wordcloud only supported for GO terms
                           doORA = T) # do ora per cluster


# let's say we are interested in exploring cluster 2 in plotunique. Lets break up this cluste for further analysis 

plotoptimalcluster2 <- OptimalGeneSets(Object = GSEA.Object3, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                cluster = 2, # which cluster
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters in cluster 1")

plotoptimalcluster2 # optimal 2 break up cluster 2 in 2 clusters

GSEA.Object3breakup <- BreakUpCluster(GSEA.Object3, 
                                      breakup.cluster = 2, # which cluster
                                      sub.cluster = 2, # in how many cluster split up
                                      uniquePathways = TRUE) # conside unique pathways

plotuniquebreakup <- PlotGeneSets(GSEA.Object3breakup, 
                                  uniquePathways = TRUE, 
                                  wordcloud = FALSE, # wordcloud only supported for GO terms
                                  doORA = T) # do ora per cluster

plotuniquebreakup

# Now break up the cluster 1 
plotoptimalcluster1 <- OptimalGeneSets(Object = GSEA.Object3, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                cluster = 1, # which cluster
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters in cluster 1")

plotoptimalcluster1 # optimal 1 break up cluster 1 in 9 clusters

GSEA.Object3breakup2 <- BreakUpCluster(GSEA.Object3breakup, 
                                      breakup.cluster = 1, # which cluster
                                      sub.cluster = 9, # in how many cluster split up
                                      uniquePathways = TRUE) # conside unique pathways

plotuniquebreakup2 <- PlotGeneSets(GSEA.Object3breakup2, 
                                   uniquePathways = TRUE, 
                                   wordcloud = FALSE, # wordcloud only supported for GO terms
                                   doORA = T) # do ora per cluster

plotuniquebreakup2


```


```{r explore results}
# plot results for both all pathways and unique pathways
plotnounique <- PlotGeneSets(GSEA.Object3, 
                             uniquePathways = FALSE, 
                             wordcloud = FALSE, # wordcloud only supported for GO terms
                             doORA = T) # do ora per cluster

plotunique <- PlotGeneSets(GSEA.Object3, 
                           uniquePathways = TRUE, 
                           wordcloud = FALSE, # wordcloud only supported for GO terms
                           doORA = T) # do ora per cluster


# let's say we are interested in exploring cluster 2 in plotunique. Lets break up this cluste for further analysis 

plotoptimalcluster2 <- OptimalGeneSets(Object = GSEA.Object3, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                cluster = 2, # which cluster
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters in cluster 1")

plotoptimalcluster2 # optimal 2 break up cluster 2 in 2 clusters

GSEA.Object3breakup <- BreakUpCluster(GSEA.Object3, 
                                      breakup.cluster = 2, # which cluster
                                      sub.cluster = 2, # in how many cluster split up
                                      uniquePathways = TRUE) # conside unique pathways

plotuniquebreakup <- PlotGeneSets(GSEA.Object3breakup, 
                                  uniquePathways = TRUE, 
                                  wordcloud = FALSE, # wordcloud only supported for GO terms
                                  doORA = T) # do ora per cluster

plotuniquebreakup

# Now break up the cluster 1 
plotoptimalcluster1 <- OptimalGeneSets(Object = GSEA.Object3, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                cluster = 1, # which cluster
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters in cluster 1")

plotoptimalcluster1 # optimal 1 break up cluster 1 in 9 clusters

GSEA.Object3breakup2 <- BreakUpCluster(GSEA.Object3breakup, 
                                      breakup.cluster = 1, # which cluster
                                      sub.cluster = 9, # in how many cluster split up
                                      uniquePathways = TRUE) # conside unique pathways

plotuniquebreakup2 <- PlotGeneSets(GSEA.Object3breakup2, 
                                   uniquePathways = TRUE, 
                                   wordcloud = FALSE, # wordcloud only supported for GO terms
                                   doORA = T) # do ora per cluster

plotuniquebreakup2


```


```{r breakup cluster number 1}
# let's say we are interested in exploring cluster 2 in plotunique. Lets break up this cluste for further analysis 

plotoptimalcluster2 <- OptimalGeneSets(Object = GSEA.Object3, 
                uniquePathway = TRUE, # consider all the pathways (also repeated) or the unique pathways
                cluster = 2, # which cluster
                method = "silhouette", max_cluster= 24, cluster_method = "kmeans", main= "Kmeans for 24 clusters in cluster 1")

plotoptimalcluster2 # optimal 2 break up cluster 2 in 2 clusters

GSEA.Object3breakup <- BreakUpCluster(GSEA.Object3, 
                                      breakup.cluster = 2, # which cluster
                                      sub.cluster = 2, # in how many cluster split up
                                      uniquePathways = TRUE) # conside unique pathways

plotuniquebreakup <- PlotGeneSets(GSEA.Object3breakup, 
                                  uniquePathways = TRUE, 
                                  wordcloud = FALSE, # wordcloud only supported for GO terms
                                  doORA = T) # do ora per cluster

plotuniquebreakup
```
